\textbf{universal corpus}

### 2014-04-25 docs/computEL-final/clean.tex
Tidied tex files
(I have removed some commented sections that are unlikely to be included
again.  They are of course still available in the old commits.)

\paragraph{UDHR.} Although there is a pre-compiled version of the UDHR data from the
Natural Language ToolKit (NLTK) corpora
distribution,\footnote{\url{http://nltk.googlecode.com/svn/trunk/nltk_data/index.xml}}
the distribution is laden with encoding problems. 
%during their
%conversion from pdf to plaintext format. 
Instead, we use the
plaintext files available from the Unicode
website,\footnote{\url{http://unicode.org/udhr/d}} which are free of
encoding issues. The first four lines of each file record metadata,
and the rest is the translation of the UDHR. This dataset is
extremely clean, and simply required segmentation into sentences.

@@

% \begin{minipage}{\columnwidth}
% \quad 21 a.\quad o lesu mai \\
% \indent \qquad\qquad 2sg return here \\
% \indent \qquad\qquad `\emph{You return here.}' \\
% %\caption{Fijian IGT from ODIN.} 
% \end{minipage}

@@

% \begin{minipage}{\columnwidth}
% \begin{lstlisting}[language=XML]
% <igt>
%   <example>
%     <line>21 a. o lesu mai</line>
%     <line>2sg return here</line>
%     <line>`You return here.'</line>
%   </example>
% </igt>
% \end{lstlisting} 
% \centerline{Figure 2: Fijian IGT in ODIN's XML format.}
% \end{minipage}

@@

% \begin{minipage}{\columnwidth}
% \begin{lstlisting}[language=XML]
% <igt>
%   <example>
%     <line>(69) na-Na-tmi-kwalca-t 
%     Yimas (Foley 1991)</line>
%     <line>3sgA-1sgO-say-rise-PERF
%     </line>
%     <line>`She woke me up' 
%     (by verbal action)</line>
%   </example>
% </igit>
% \end{lstlisting} 
% \smallskip
% \centerline{Figure 3: Yimas IGT in ODIN's XML format.}
% \end{minipage}

@@

% \begin{minipage}{\columnwidth}
% \begin{itemize}
% \item \emph{Cleaner}: Removed (i) all heading and trailing text embedded in square or rounded brackets and (ii) heading double character token ending with bracket or fullstop.
% \begin{itemize}
% \item[(i)]
% \begin{Verbatim}
% ^(?\s?\w{1,5}\s*[):.]\s*
% \end{Verbatim}
% \item[(ii)] 
% \begin{Verbatim}
% [\[\(].{1,}[\]\)]
% \end{Verbatim}
% \end{itemize}
% \item \emph{Cleanest}: Only source lines without punctuation.
% \end{itemize}
% \end{minipage}

>>>>

\paragraph{UDHR.} Although there is a pre-compiled version of the UDHR data in the Natural Language ToolKit (NLTK) corpora distribution,\footnote{\url{http://nltk.googlecode.com/svn/trunk/nltk_data/index.xml}}
the distribution is laden with encoding problems. Instead, we used the plaintext files available from the Unicode website,\footnote{\url{http://unicode.org/udhr/d}} which are free from encoding issues. The first four lines of each file record metadata, and the rest is the translation of the UDHR. This dataset is extremely clean, and simply required segmentation into sentences.

@@

@@

@@

@@

### 2014-04-25 docs/computEL-final/data.tex
Tidied tex files
(I have removed some commented sections that are unlikely to be included
again.  They are of course still available in the old commits.)

% \begin{enumerate}
% \item The Online Database of Interlinear Text (ODIN)
% \item The Omniglot website
% \item The Universal Declaration of Human Rights (UDHR)
% \item Wikipedia
% \end{enumerate}

@@

% \begin{itemize}[noitemsep]
% \item \url{www.omniglot.com/language/phrases/*} 
% \item \url{www.omniglot.com/babel/*}
% \end{itemize}

@@

One benefit of this approach is that glossed texts are treated in exactly the same way as parallel texts.  There is a unique identifier for each morpheme, and glosses are stored under this identifier and the corresponding gloss code.  Furthermore, to motivate the important place of parallel texts in a universal corpus, Abney and Bird view translations into a high-resource reference language as convenient surrogates of meaning. By the same reasoning, we can use glosses to provide a more detailed surrogate of meaning, only written in a metalanguage instead of a natural one.

@@

%\begin{table}
%\centering
%    \begin{tabular}{l|cc}
%    ~         				& \#Languages & \#Families \\ \hline
%    ODIN      				& 1218       & 101       \\
%    Omniglot  				& 134        & 21        \\
%    UDHR      				& 355        & 47        \\
%    Wikipedia 				& 209        & 22       \\ \hline
%    \textbf{Combined}	& 1347			 & 106 
%    \end{tabular}
%\caption{Corpus Coverage}
%\end{table}

>>>>

@@

@@

One benefit of this approach is that glossed texts are treated in exactly the same way as parallel texts.  There is a unique identifier for each morpheme, and glosses are stored under this identifier and the corresponding gloss code.  Furthermore, to motivate the important place of parallel texts in a universal corpus, Abney and Bird view translations into a high-resource reference language as a convenient surrogate of meaning. By the same reasoning, we can use glosses to provide a more detailed surrogate of meaning, only written in a metalanguage instead of a natural one.

@@
